Geophysicists should use the gravity disturbance rather than the gravity anomaly

### 2018-05-18 manuscript/letter.tex
Simplify the figure captions by removing redundancy
A lot of the definitions are in the text already so we don't need to
repeat them.

\begin{figure}
%    \vspace{5.5cm}
    \includegraphics{figures/cartesian-geodetic-systems.png}
    \caption{Schematic representation of the Geocentric Cartesian System (GCS) and the Geocentric Geodetic System (GGS). The GCS has the $Z$-axis coincident with the mean Earth's rotational axis,
    the $X$-axis pointing to the Greenwich meridian and the $Y$-axis
    directed so as to obtain a right-handed system. The GGS is      defined by an oblate ellipsoid with semi-minor axis $b$,
    coincident with the $Z$-axis of GCS, and a semi-major
    axis $a$. In this coordinate system, the position of a point is
    determined by the geometric height $h$, geodetic latitude
    $\varphi$ and longitude $\lambda$.
    The Earth's center of mass is represented
    by $O$, $P$ represents a point $(h_{P}, \varphi_{P}, \lambda_{P})$ and $P^{\prime}$ its projection onto the plane $XY$
    (Equatorial plane). The plane containing $O$, $P$ and
    $P^{\prime}$ is represented in gray in (a) and (b).
    The unit vectors $\versor{u}_{P}$, $\versor{v}_{P}$ and
    $\versor{w}_{P}$ define three mutually orthogonal
    directions at $P$ (eq. \ref{eq:unit-vectors}).
    In (b), $Q$ represents a point $(h_{Q}, \varphi_{Q}, \lambda_{Q})$,
    which is the projection of $P$ onto the reference ellipsoid, at
    the same latitude and longitude ($\varphi_{Q} = \varphi_{P}$ and $\lambda_{Q} = \lambda_{P}$).}
  \label{fig:GCS-GGS}
\end{figure}

\begin{figure}
    \includegraphics{figures/local-system.png}
    \caption{(a) Schematic representation of a topocentric Cartesian
    coordinate system (TCS) with origin at a point $P$. The axes $x$
    and $y$ are parallel to the unit vectors $\versor{v}_{P}$
    and $\versor{w}_{P}$ (eq. \ref{eq:unit-vectors} and
    Fig. \ref{fig:GCS-GGS}), respectively. On the other hand, the $z$ axis is opposite to the unit vector $\versor{u}_{P}$ (eq.
    \ref{eq:unit-vectors} and Fig. \ref{fig:GCS-GGS}) and points downward. The gray plane is the same shown in Fig. \ref{fig:GCS-GGS}.
    (b) Schematic representation of the gravity vector
    $\vector{g}_{P}$, normal gravity vector $\vector{\gamma}_{P}$,
    gravity disturbance vector $\delta \vector{g}_{P}$
    (eq. \ref{eq:gravity-disturbance-vector}) and unit vector
    $\versor{u}_{P}$ (eq. \ref{eq:unit-vectors}) at a point
    $P$.}
  \label{fig:TCS}
\end{figure}

\begin{figure}
    \includegraphics{figures/surfaces.png}
    \caption{Schematic representation of the gravity vector
        $\vector{g}_{P}$, normal gravity vector $\vector{\gamma}_{P}$,
        gravity disturbance vector $\delta \vector{g}_{P}$
        (eq. \ref{eq:gravity-disturbance-vector}), unit vector
        $\versor{u}_{P}$ (eq. \ref{eq:unit-vectors}) at a point $P$
        on the surface of the Earth, gravity vector $\vector{g}_{Q^{\prime}}$
        at a point $Q^{\prime}$ on the Geoid, normal gravity vector
        $\vector{\gamma}_{Q}$ at a point $Q$ on the reference ellipsoid,
        geometric height $h$, orthometric height $H$ and geoidal undulation
        $N$ \citep{heiskanen-moritz1967}.
        The dashed line passing through
        $Q$, $Q^{\prime}$ and $P$ is normal to the
        surface of the reference ellipsoid at $Q$. This figure
        shows a commonly used approximation in which the ellipsoid
        surface and the Geoid are represented as parallel surfaces,
        so that $h \approx H + N$.}
  \label{fig:surfaces}
\end{figure}

>>>>

\begin{figure}
%    \vspace{5.5cm}
    \includegraphics{figures/cartesian-geodetic-systems.png}
    \caption{
    The Geocentric Cartesian System (GCS) and the Geocentric Geodetic System
    (GGS).
    The GGS is defined by an oblate ellipsoid with semi-minor axis $b$ and
    semi-major axis $a$.
    In this coordinate system, the position of a point is determined by the
    geometric height $h$, geodetic latitude $\varphi$, and longitude $\lambda$.
    $O$ is the Earth's center of mass, $P$ is an observation point, and
    unit vectors $\versor{u}$, $\versor{v}$, and $\versor{w}$ define mutually
    orthogonal directions at $P$ (eq. \ref{eq:unit-vectors}).
    In (b), $Q$ is the projection of $P$ onto the reference ellipsoid at
    the same latitude and longitude.
    }
  \label{fig:GCS-GGS}
\end{figure}

\begin{figure}
    \includegraphics{figures/local-system.png}
    \caption{
    (a) The topocentric Cartesian coordinate system (TCS) with origin at a
    point $P$.
    Axes $x$ and $y$ are parallel to the unit vectors $\versor{v}$ and
    $\versor{w}$ (eq. \ref{eq:unit-vectors} and Fig. \ref{fig:GCS-GGS}),
    respectively, and the $z$ axis is opposite to $\versor{u}$.
    The gray plane is the same shown in Fig. \ref{fig:GCS-GGS}.
    (b) Schematic representation of the gravity vector
    $\vector{g}_{P}$, normal gravity vector $\vector{\gamma}_{P}$,
    gravity disturbance vector $\delta \vector{g}_{P}$
    (eq. \ref{eq:gravity-disturbance-vector}) and unit vector
    $\versor{u}_{P}$ (eq. \ref{eq:unit-vectors}) at a point
    $P$.
    }
  \label{fig:TCS}
\end{figure}

\begin{figure}
    \includegraphics{figures/surfaces.png}
    \caption{
    The gravity vector
    $\vector{g}_{P}$, normal gravity vector $\vector{\gamma}_{P}$,
    gravity disturbance vector $\delta \vector{g}_{P}$
    (eq. \ref{eq:gravity-disturbance-vector}), and unit vector
    $\versor{u}_{P}$ (eq. \ref{eq:unit-vectors}) at a point $P$
    on the surface of the Earth.
    The gravity vector $\vector{g}_{Q^{\prime}}$
    at a point $Q^{\prime}$ on the geoid, normal gravity vector
    $\vector{\gamma}_{Q}$ at a point $Q$ on the reference ellipsoid,
    geometric height $h$, orthometric height $H$, and geoidal height $N$.
    The dashed line passing through
    $Q$, $Q^{\prime}$ and $P$ is normal to the
    surface of the reference ellipsoid at $Q$.
    This figure shows a commonly used approximation in which the ellipsoid and
    geoid are represented as parallel surfaces so that $h \approx H + N$.
    }
  \label{fig:surfaces}
\end{figure}
